% vim:ts=4:sw=4
% Copyright (c) 2014 Casper Ti. Vector
% Public domain.

\begin{cabstract}

脉冲星类致密天体是宇宙中可直接观测的最致密的天体。它们不仅有丰富的多波段的观测现象，
还对于基础物理的研究有重要意义。除了可以用于检验引力理论，脉冲星类致密天体的结构
和状态方程直接反应了致密物质的物态、强相互作用以及QCD相变的本质。在我攻读博士学位
期间，我在北京大学和CSIRO Astronomy and Space Science展开了对于脉冲星类致密天体的
多波段的研究。

我的研究的主要部分是关于射电脉冲星，尤其是射电脉冲星的高精度测时和脉冲星测时阵列
（pulsar timing array, PTA）。使用Parkes Pulsar Timing Array的数据，我们研究了24颗
毫秒脉冲星的多波段的脉冲偏振轮廓。对毫秒脉冲星的脉冲偏振轮廓的了解是高精度测时的
基础，同时也为脉冲星辐射机制的研究提供了素材。为了提高脉冲星的测时精度，并且理解
多种与频率相关的效应，比如星际闪烁和色散延迟，对脉冲星测时精度的影响，我们开发了新
的脉冲星模拟和测时软件。我们还讨论了五百米口径球面望远镜（Five-hundred-meter Aperture 
Spherical Telescope）对于未来脉冲星测时阵列研究的贡献。

为了寻找新的测量脉冲星质量的方法，我们研究了由中子星和射电脉冲星导致的微引力透镜
事件的性质。我们讨论了未来的大型望远镜发现由射电脉冲星导致的astrometric microlensing
事件的可能性。我们的结果显示，通过astrometric microlensing现象，我们可以较精确
地测量脉冲星的质量。假设脉冲星的距离可以通过射电观测限制，那么脉冲星的质量可以
测量精确到约10\%。在X射线波段，我们研究了反常X射电脉冲星和软伽马射线重复爆
的硬X射电谱，同时我们的模拟显示未来的硬X射线望远镜，例如硬X射线调制望远镜（Hard 
X-ray Modulation Telescope，HMXT）有望帮助我们区分不同的辐射模型。
	\pkuthssffaq
\end{cabstract}

\begin{eabstract}

Pulsar-like compact objects as the densest observable objects in the Universe, 
are not only important in understanding diverse astrophysical phenomena, but 
also significant in fundamental physics. Besides the physics of gravity, the 
answer to the question that whether pulsar-like compact stars are neutron stars 
or quark stars would have profound implications on the physics of condensed 
matter, the nature of strong interaction as well as QCD phase transition. During 
my PhD study at Peking University and CSIRO Astronomy and Space Science, I 
carried out multi-wavelength researches on pulsar-like compact objects. 

The main part of my study is focused on radio pulsars, especially on high precision 
timing of radio pulsars and pulsar timing arrays (PTAs). Using the Parkes Pulsar 
Timing Array data sets, we studied the multi-frequency polarization pulse profiles 
of 24 millisecond pulsars. We developed new simulation and timing software packages 
to investigate various frequency-dependent effects on the precision of pulsar timing, 
including interstellar scintillation and dispersive delay. We also studied how the 
Five-hundred-meter Aperture Spherical Telescope can contribute to the PTA studies. 

To find new ways to measure pulsar masses, we investigated properties of Galactic 
microlensing events caused by neutron stars and pulsars. We describe a possible 
study of astrometric microlensing events using radio pulsars that are likely to 
be discovered by future large telescopes. We show that such a study could lead 
to precise measurements of pulsar masses. For instance, if a pulsar distance could 
be constrained through radio observations, then its mass would be determined with 
a precision of $\sim$10\%. In the X-ray band, we studied the hard X-ray spectrum 
of AXPs and SGRs using XMM-Newton, Suzaku and INTEGRAL data and how that future 
hard X-ray telescopes, such as the Hard X-ray Modulation Telescope, would be 
able to distinguish different models. 

\end{eabstract}

