% vim:ts=4:sw=4
% Copyright (c) 2014 Casper Ti. Vector
% Public domain.

\chapter{发表文章列表}

\begin{enumerate}
\item R. M. Shannon and 22 co-authors including \textbf{S. Dai},
``Gravitational waves from binary supermassive black holes missing in pulsar observations", 
\textsl{Science}, submitted.

\item \textbf{S. Dai}, G. Hobbs, R. N. Manchester, \textsl{et al}.
``A Study of Multi-frequency Polarization Pulse Profiles of Millisecond Pulsars",
\textsl{MNRAS}, 2015, 449, 3223.
			    
\item \textbf{S. Dai}, M. C. Smith, M. X. Lin, Y. L. Yue, G. Hobbs, R. X. Xu,
``Gravitational Microlensing of Neutron Star and Radio Pulsars: Event Rates, Time-scale Distributions and Mass Measurements",
\textsl{ApJ}, 2015, 802, 120.

\item J. B. Wang and 19 co-authors including \textbf{S. Dai},
``Searching for Gravitational Wave Memory Bursts with the Parkes Pulsar Timing Array", 
\textsl{MNRAS}, 2015, 446, 1657.

\item G. J. Guo, \textbf{S. Dai}, Z. S. Li, \textsl{et al}.
``To Understand the X-ray Spectrum of Anomalous X-ray Pulsars and Soft Gamma-ray Repeaters",
\textsl{RAA}, 2015, 15, 525.

\item Z. J. Qu, Z. S. Li, Y. P. Chen, \textbf{S. Dai}, L. Ji, R. X. Xu, S. Zhang,
``Analysis of Short Bursts in SGR 1806-20, 1E 1048-5937 and SGR 0501+4516",
\textsl{PASA}, 2015, 127, 211.

\item G. Hobbs, \textbf{S. Dai}, R. N. Manchester, R. M. Shannon, M. Kerr, K. J. Lee, R. X. Xu,
``The Role of FAST in Pulsar Timing Arrays",
\textsl{RAA, a special issue on FAST}, 2014, accepted, arXiv:1407.0435

\item X. J. Zhu and 18 co-authors including \textbf{S. Dai},
``An All-sky Search for Continuous Gravitational Waves in the Parkes Pulsar Timing Array Data Set", 
\textsl{MNRAS}, 2014, 444, 3709.

\item R. M. Shannon, S. Os{\l}owski, \textbf{S. Dai}, \textsl{et al}.
``Limitations in Timing Precision due to Single-pulse Shape Variability in Millisecond Pulsars",
\textsl{MNRAS}, 2014, 443, 1463.

\item T. Dolch and 42 co-authors including \textbf{S. Dai},
``A 24 Hr Global Campaign to Assess Precision Timing of the Millisecond Pulsar J1713+0747", 
\textsl{ApJ}, 2014, 794, 21.

\item \textbf{S. Dai}, L. X. Li and R. X. Xu,
``The Plateau of Gamma-ray Burst: Hint for the Solidification of Quark Matter?'',
\textsl{Science China G: Physics, Mechanics \& Astronomy}, 2011, 54, 1541.

\item \textbf{S. Dai}, R. X. Xu and A. Esamdin,
``Microlensing Pulsars'',
\textsl{MNRAS}, 2010, 405, 2754.

\end{enumerate}

\pkuthssffaq

